\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
shortened title across the top of the page

\newcommand{\titleName}{General-Purpose GPUs and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

% Page heads
\markboth{C. Smith}{\titleName{}}

% Title portion
\title{\titleName{}}
\author{Connor Smith
\affil{Brigham Young University}}

@@

\acmformat{\titleName{}.}

>>>>

\newcommand{\titleNameLong}{General-Purpose GPUs and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

\newcommand{\titleNameShort}{GPGPU and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

% Page heads
\markboth{C. Smith}{\titleNameShort{}}

% Title portion
\title{\titleNameLong{}}
\author{Connor Smith
\affil{Brigham Young University}}

@@

\acmformat{\titleNameLong{}.}
